A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-07-23 Article.qmd
move simu_data function to dedicated file so that it can also be used outiside of article

```{r dependancies, cache = FALSE, include = FALSE}
library(ggplot2);   library(tidyverse);   library(gridExtra);   library(rjags);   
library(latex2exp);   library(grid);   library(dplyr);   library(tidyr);   library(tibble)

@@

```{r simulations, cache = FALSE, eval = TRUE, results = 'hide'}
# The following code presents the inference for one seed. As the calculus 
# time is growing fast with the number of trials and the number of sampled
# values, we set here the number of trials to 10 (I = 10) and the number
# of adaptations and iterations to 2000.

@@

simu_data <- function(seed, I){

    set.seed(seed)

    ID = c(1 : I);

    data = expand_grid(ID = c(1 : I),   Block = c(1 : K),   Band = c(1 : J), 
                   Beet = c(1 : N),   DPT = seq(0, 12, length.out = T))

    data = data %>% 
        mutate(Insecticide = ifelse(DPT <= 0, "T 1", paste("T", Band)),
               tscaled = scale(data$DPT)) %>% 
        mutate(st = paste(ID, Insecticide), 
               sbit = paste(ID, Block, Insecticide, DPT))

    Insecticide = data$Insecticide %>% unique %>% sort
    names(gamma0) = Insecticide
    names(gamma1) = Insecticide

    beta0 = rnorm(I, sd = sig0);   
    u = rnorm(I * J, sd = chi);   
    epsi = rnorm(I * J * K * (T - 1) + I * K, sd = eta);

    names(beta0) = data$ID %>% unique;   
    names(u) = data$st %>% unique
    names(epsi) = data$sbit %>% unique

    data = data %>% mutate(alpha0 = alpha0,
                           alpha1 = alpha1,
                           N = N,
                           beta0 = recode(ID, !!!beta0),
                           gamma0 = recode(Insecticide, !!!gamma0), 
                           gamma1 = recode(Insecticide, !!!gamma1),
                           u = recode(st, !!!u),
                           epsi = recode(sbit, !!!epsi))

    data$lb = exp(data$alpha0 + data$beta0 + data$gamma0 + (data$alpha1 + 
              data$gamma1) * data$tscaled + data$u + data$epsi)

    data$W = sapply(c(1 : (I * J * K * T * N)), 
                    function(x) rpois(1, data$lb[x]))

    dataYZ = data %>% group_by(ID, Block, Band, DPT) %>% 
        summarise(Insecticide = unique(Insecticide), 
                  tscaled = unique(tscaled), st = unique(st), N = unique(N), 
                  Y = sum(W), Z = sum(W > 0)) %>% as.data.frame

    dataW = data %>% select(- alpha0, - alpha1, - beta0, - gamma0, - gamma1, 
                            - u, - epsi, - lb)

    return(list("dataYZ" = dataYZ, "dataW" = dataW))
}                        
############################################################################

>>>>

```{r dependencies, cache = FALSE, include = FALSE}
library(ggplot2);
library(tidyverse);
library(gridExtra);
library(rjags);
library(latex2exp);
library(grid);
library(dplyr);
library(tidyr);
library(tibble)

@@

```{r simulation-function}
#| echo: true
#| eval: true 
#| file: functions/simu_data.R 
```

```{r simulations, cache = TRUE, eval = TRUE, results = 'hide'}
# The following code presents the inference for one seed. As the calculus 
# time is growing fast with the number of trials and the number of sampled
# values, we set here the number of trials to 10 (I = 10) and the number
# of adaptations and iterations to 2000.

@@

############################################################################
